Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-13 csf-2017/paper.tex
put list of possible examples in a comment
Try to make a sentence compute...

The basic idea of our approach is quite simple: we stick to a single, rather
standard C stack and register-passed return pointers in much the same way as a
standard C ABI\lau{This sentence does not compute}. However, to prevent various ways of misusing this basic scheme,
we put local capabilities to work and take a number of not-always-obvious safety
measures. In the next paragraphs, we will explain the issues to be considered in
all the relevant situations: when (1) starting our program, (2) Returning to the
adversary, (3) invoking the
adversary, (4) returning from the adversary, (5) invoking an adversary callback
and (6) having a callback invoked by the adversary.

>>>>

The basic idea of our approach is quite simple: we stick to a single, rather
standard, C stack and register-passed return pointers, much like a standard C
ABI\lau{This sentence does not compute}. However, to prevent various ways of
misusing this basic scheme, we put local capabilities to work and take a number
of not-always-obvious safety measures. In the next paragraphs, we will explain
the issues to be considered in all the relevant situations: when (1) starting
our program, (2) Returning to the adversary, (3) invoking the adversary, (4)
returning from the adversary, (5) invoking an adversary callback and (6) having
a callback invoked by the adversary.
